Supplementary Materials

### 2020-06-18 analysis/analysis2.Rmd
updated subgroup table
Subgroup comparison by symmetry model.
Why are the results odd?
trying to work out why there's no main effect of rotation

options(mc.cores = parallel::detectCores())
```

@@

>>>>

# options(mc.cores = parallel::detectCores())
```

@@

## Modelling by Subgroup

```{r}
source("scripts/get_subgroup_comparisons.R")

subgroup_comp$eeg <- get_subgroup_comparisons2(my_samples$eeg, sym_dat)

subgroup_comp$eeg %>% group_by(key) %>%
  summarise(
    index = unique(index),
    d_ref = unique(d_ref),
    d_rot = unique(d_rot),
    d_gli = unique(d_gli),
    value = mean(value)
  ) -> comp_info

m <- brm(data = comp_info, value ~ d_rot + d_ref + d_gli)

```{r}
summary(m)

knitr::kable(comp_info) %>% kableExtra::kable_styling()

comp_info %>% filter(d_ref == 0, d_gli == 0) %>% ggplot(aes(x = d_rot, y = value, label = key)) + geom_point() + geom_smooth(method = "lm") + ggtitle("rotations only: no reflections or glides")+ ggrepel::geom_label_repel()

comp_info %>% filter(d_rot == 0, d_gli == 0) %>% ggplot(aes(x = d_ref, y = value, label = key)) + geom_point() + geom_smooth(method = "lm") + ggtitle("reflections only: no rotations or glides")+ ggrepel::geom_label_repel()

comp_info %>% filter(d_ref == 0) %>% ggplot(aes(x = d_rot, y = value, label = key)) + geom_point() + geom_smooth(method = "lm") + ggtitle("no reflections") + ggrepel::geom_label_repel()

comp_info %>% filter(d_rot == 0) %>% ggplot(aes(x = d_ref, y = value, label = key)) + geom_point() + geom_smooth(method = "lm") + ggtitle("no rotations")+ ggrepel::geom_label_repel()
